DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car

### 2018-01-24 paper/conclusion.tex
Add initial cache partition section
Also made minor changes in other sections of the paper, and added the
script used to max performance on the TX2.

As future work, we plan to apply shared resource management
techniques~\cite{Yun2013,yun2014rtas} on the DeepPicar platform and
evaluate their impact on the real-time performance of the system. We
also plan to improve the prediction accuracy by feeding more data and
upgrading the RC car hardware platform to enable more precise steering
angle control.

>>>>

As future work, we plan to apply shared DRAM resource management
techniques~\cite{Yun2013,yun2014rtas} on the DeepPicar platform and
evaluate their impact on the real-time performance of the system. We
also plan to improve the prediction accuracy by feeding more data and
upgrading the RC car hardware platform to enable more precise steering
angle control.

### 2018-01-24 paper/evaluation.tex
Change figure sizes
Many of the figures were relatively small and hard to see, so the sizes
were increased.
Add initial cache partition section
Also made minor changes in other sections of the paper, and added the
script used to max performance on the TX2.

\begin{figure}[t]
  \centering
  \includegraphics[width=.5\textwidth]{figs/Fig7_new}
  \caption{DeepPicar's control loop processing times over 1000 input image frames.}
  \label{fig:control-loop-timing}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{figs/perf_vs_corecnt}
  \caption{Average control loop execution time vs. \#of CPU
    cores.}
  \label{fig:perf-vs-corecnt}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{figs/perf_vs_modelcnt}
  \caption{Timing impact of co-scheduling multiple DNNs. 1Nx1C: one DNN
    model using one core; 4Nx1C: four DNN models each using one core;
    1Nx2C: one DNN model using two cores; 2Nx2C: two DNN models each
    using two cores.} 
  \label{fig:perf-vs-modelcnt}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{figs/l2missrate_vs_modelcnt}
  \caption{L2 cache miss rates of different neural network and core
    assignments. X-axis is the same as Figure~\ref{fig:perf-vs-modelcnt}.} 
  \label{fig:l2missrate-vs-modelcnt}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{figs/perf_vs_bandwidth}
  \caption{Effect of memory performance hogs on the DNN
    inferencing. The DNN model uses Core 0 and memory-hog co-runners
    use the rest of the cores.}
  \label{fig:}
\end{figure}

@@

\begin{table*}[h]
  \centering
  \begin{tabular}{|c|c|c|c|}
    \hline
    Item    & Raspberry Pi 3 (B)   & Intel UP                  & NVIDIA Jetson TX2\\
    \hline
            & BCM2837              & X5-Z8350 (Cherry Trail)   & Tegra X2 \\
    CPU     & 4x Cortex-A53@1.2GHz/512KB L2  &
              4x Atom@1.92GHz/2MB L2 &
              4x Cortex-A57@2GHz/2MB L2 \\
            &              &              & 2x Denver@2.0GHz/2MB L2 (not used)  \\
    \hline
    GPU     &  VideoCore IV (not used)    &
               Intel HD 400 Graphics (not used) &
               Pascal 256 CUDA cores   \\
    \hline
    Memory  & 1GB LPDDR2   &  2GB DDR3L     & 8GB LPDDR4              \\
    \hline
  \end{tabular}
  \caption{Compared embedded computing platforms}
  \label{tbl:platforms}
\end{table*}

@@

Lastly, we find that consolidating memory (DRAM) performance
intensive applications could jeopadize DNN performance, because DNN
performance appears to be very sensitive to memory performance; we observe up
to 9.6X slowdown in DNN performance by co-scheduling synthetic memory 
bandwidth intensive applications on idle cores.

>>>>

\begin{figure}[t]
  \centering
  \includegraphics[width=.75\textwidth]{figs/Fig7_new}
  \caption{DeepPicar's control loop processing times over 1000 input image frames.}
  \label{fig:control-loop-timing}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.7\textwidth]{figs/perf_vs_corecnt}
  \caption{Average control loop execution time vs. \#of CPU
    cores.}
  \label{fig:perf-vs-corecnt}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.7\textwidth]{figs/perf_vs_modelcnt}
  \caption{Timing impact of co-scheduling multiple DNNs. 1Nx1C: one DNN
    model using one core; 4Nx1C: four DNN models each using one core;
    1Nx2C: one DNN model using two cores; 2Nx2C: two DNN models each
    using two cores.} 
  \label{fig:perf-vs-modelcnt}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.7\textwidth]{figs/l2missrate_vs_modelcnt}
  \caption{L2 cache miss rates of different neural network and core
    assignments. X-axis is the same as Figure~\ref{fig:perf-vs-modelcnt}.} 
  \label{fig:l2missrate-vs-modelcnt}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.7\textwidth]{figs/perf_vs_bandwidth}
  \caption{Effect of memory performance hogs on the DNN
    inferencing. The DNN model uses Core 0 and memory-hog co-runners
    use the rest of the cores.}
  \label{fig:}
\end{figure}

@@

\subsection{Effect of Cache Partitioning}

In order to determine if the DNN is mostly affected by shared DRAM 
contention, we partition the L2 cache of the Pi3 and reperform the 
same experiments to see if there are any noticable changes. For the 
partition, we employ PALLOC~\cite{yun2014rtas}, a color-based page 
allocator that works on the kernel level. For the bit mask, we select 
bits 12, 13 and 14 as those bits are used to specifically access the 
shared L2 cache, as can be seen by \ref{fig:cache-mapping}. This 
results in 2\textsuperscript{3} = 8 colors, which we then assign to the Pi3's 
physical cores such that each core has two unique colors (colors 0 
and 1 are assigned to core 0, colors 2 and 3 are assigned to core 1, 
etc.).

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{figs/cache-mapping}
  \caption{A memory mapping of the cache sets for the Broadcom 
BCM2837 processor used in the Raspberry Pi 3 Model B.}
  \label{fig:cache-mapping}
\end{figure}

If performance improves as a result of partitioning the shared cache 
then we know that the DNN, to some extent, relies on shared cache 
performance in addition to shared DRAM performance. On the other 
hand, if there is no improvement in performance, then it can be 
observed that the shared memory is more critical to the performance 
of the DNN.

\begin{figure}[h]
  \centering
  \includegraphics[width=.7\textwidth]{figs/palloc_multicore}
  \caption{Average control loop execution time vs. \#of CPU
    cores with cache partitioning enabled.}
  \label{fig:palloc_multicore}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=.7\textwidth]{figs/palloc_multicore}
  \caption{Timing impact of co-scheduling multiple DNNs when cache 
partitioning is enabled.}
  \label{fig:palloc_multimodel}
\end{figure}

The results can be seen in Figures \ref{fig:palloc_multicore} - 
\ref{fig:palloc_bandwidth_l2missrate}. As 
expected, based off of previous results, we find that the performance 
of the DNN remains consistent when cache partitioning is employed. 
When fewer cores are used, DNN performance is slightly affected as 
the entire L2 cache isn't available to the network. In the case of 
running multiple models simultaneously, no performance improvements 
are seen, which further shows that the shared cache has no affect on 
the DNN's real-time performance.

\begin{figure}[h]
  \centering
  \includegraphics[width=.7\textwidth]{figs/palloc_bandwidth_exectime}
  \caption{Timing impact of co-scheduling memory intensive co-runners 
when cache partitioning is enabled.}
  \label{fig:palloc_bandwidth_exectime}
\end{figure}

In the case of running the DNN alongside synthetic memory-intensive 
benchmarks, however, we found that partitioning the L2 cache led to a 
decrease in performance as the number of co-runners increased. 
However, the L2 miss rates of the model decrease as more benchmarks 
are introduced. As such, this means that the model encounters greater 
interence from the memory contention of the co-runners.

\begin{figure}[h]
  \centering
  \includegraphics[width=.7\textwidth]{figs/palloc_bandwidth_l2missrate}
  \caption{L2 miss rate impact of co-scheduling memory intensive co-
runners when cache partitioning is enabled.}
  \label{fig:palloc_bandwidth_l2missrate}
\end{figure}

By partitioning the shared L2 cache, we find that no noticable 
improvements are gained and that performance remains consistent, or 
decreases, depending on the circumstances. As a result, we find that 
cache partitioning is not an effective isolation mechanism, and that 
the performance of the shared DRAM is of greater importance to the 
real-time efficiacy of the DeepPicar.

\begin{table*}[!h]
  \centering
  \begin{tabular}{|c|c|c|c|}
    \hline
    Item    & Raspberry Pi 3 (B)   & Intel UP                  & NVIDIA Jetson TX2\\
    \hline
            & BCM2837              & X5-Z8350 (Cherry Trail)   & Tegra X2 \\
    CPU     & 4x Cortex-A53@1.2GHz/512KB L2  &
              4x Atom@1.92GHz/2MB L2 &
              4x Cortex-A57@2GHz/2MB L2 \\
            &              &              & 2x Denver@2.0GHz/2MB L2 (not used)  \\
    \hline
    GPU     &  VideoCore IV (not used)    &
               Intel HD 400 Graphics (not used) &
               Pascal 256 CUDA cores   \\
    \hline
    Memory  & 1GB LPDDR2   &  2GB DDR3L     & 8GB LPDDR4              \\
    \hline
	Peak Memory Bandwidth & 8.5 GB/s & 12.8 GB/s & 59.7 GB/s \\
	\hline
	Measured Bandwidth & 2127.94 MB/s & 3951.94 MB/s & 4447.90 MB/s \\
	\hline
  \end{tabular}
  \caption{Compared embedded computing platforms}
  \label{tbl:platforms}
\end{table*}

@@

Fourth, we find that consolidating memory (DRAM) performance
intensive applications could jeopadize DNN performance, because DNN
performance appears to be very sensitive to memory performance; we 
observe up to 11.6X slowdown in DNN performance by co-scheduling 
synthetic memory bandwidth intensive applications on idle cores.

Lastly, we find that partitioning the shared L2 cache provides 
practically no benefits to the real-time performance of the DNN. To the 
contrary, performance is negatively affected when fewer cores are used, 
due to less cache being available, and memory intensive co-runners are 
introduced, as they generate more memory contention. Furthermore, we 
find that performance remains consistent when multiple models are run 
simultaneously. As such, we conclude that the shared L2 cache is not 
important to the DNN's real-time performance.

### 2018-01-24 paper/intro.tex
Add initial cache partition section
Also made minor changes in other sections of the paper, and added the
script used to max performance on the TX2.

We find that the DeepPicar is capable of 
completing control loops in under 50 ms, or 20 hz, and can do so 
almost 99\% of the time.
Other tested embedded platforms, Intel Up and NVIDIA TX2, offer even
better performance, capable of supporting deep-learning based real-time
control up to 100 Hz control frequency on the TX2 when the GPU is used.
However, in all platforms, shared resource contention remains an
important issue as we observe up to 9.6X control loop execution time
increase, mostly due to increase in the nueral network inferencing
operation, when memory performance intensive applications are
co-scheduled on idle CPU cores.

>>>>

We find that the DeepPicar is capable of 
completing control loops in under 33.$\overline{\mbox{33}}$ 
ms, or 30 hz, and can do so 100\% of the time.
Other tested embedded platforms, Intel Up and NVIDIA TX2, offer even
better performance, capable of supporting deep-learning based real-time
control up to 100 Hz control frequency on the TX2 when the GPU is used.
However, in all platforms, shared resource contention remains an
important issue as we observe up to 11.6X control loop execution time
increase, mostly due to increase in the nueral network inferencing
operation, when memory performance intensive applications are
co-scheduled on idle CPU cores.
